Evolution of the AGN UV luminosity function

### 2017-04-25 Paper/paper.tex
Update text

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{pdflscape}

@@

  We model the quasar luminosity function as a double power law given
  by \citep[e.g.,][]{2013ApJ...773...14R}
  \begin{equation}
    \phi(M) = \frac{\phi_*}{10^{0.4(\alpha+1)(M-M_*)}+10^{0.4(\beta+1)(M-M_*)}},
\label{eqn:dpl}
\end{equation}
where all magnitudes are absolute magnitudes at rest-frame 1450~{\AA}.
The luminosity function $\phi$ gives the comoving number density of
quasars per unit magnitude.  It usually has units of
mag$^{-1}$cMpc$^{-3}$.  Equation~(\ref{eqn:dpl}) has four free
parameters: the amplitude $\phi_*$, the ``break'' $M_*$, the faint-end
slope $\beta$, and the bright-end slope $\alpha$.  The likelihood
function can be written as \citep{2001AJ....121...54F}
\begin{equation}
  \mathcal{L}=\prod_{i,j}\frac{e^{-\mu_{ij}}\mu_{ij}^{n_{ij}}}{n_{ij}!},
  \label{eqn:lhood}
\end{equation}
where $n_{ij}$ is the number of quasars observed in the $(M_i, z_j)$
bin, and
\begin{equation}
  \mu_{ij}= \int_{M_i}^{M_{i+1}}dM\int_{z_i}^{z_{i+1}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
\end{equation}
is the average number of quasars expected in the $(M_i, z_j)$ bin
given the luminosity function $\phi(M,z)$.  To obtain the maximum
likelihood solution for the luminosity functin parameters, we minimise
the function
\begin{equation}
  S = -2\ln\mathcal{L}.
\end{equation}
In the limit of infinitesimal bins, $n_{ij}=0$ or $1$, in which case
Equation~(\ref{eqn:lhood}) can be simplified and we can write
\begin{multline}
  S = -2\sum_{i=1}^N\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}dM\int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
\end{multline}
where $N$ is the total number of quasars in the sample and the integral in the second term on the right hand side is now on the full range of $M$ and $z$.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{sdss.pdf}
  \end{center}
  \caption{Comparison with the published LF of
    \citet{2013ApJ...768..105M} for SDSS DR3.  There are 15,343
    quasars in this sample, of which 155 quasars have $z<0.3$ and 9
    quasars have $z>5$.  Of the remaining 15179 quasars with
    $0.3<z<5$, 60 quasars have $V_i=0$ and are dropped from the
    analysis.  As a result, the green points above contain 15,119
    quasars.  The red circles contain 14,953 quasars.}
  \label{fig:sdss}
\end{figure*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.6\textwidth,keepaspectratio]{glikman.pdf}
  \end{center}
  \caption{Comparison with the published LF of
    \citet{2011ApJ...728L..26G} for $3.5<z<5.2$.  There are 24 
    quasars in their two samples (NDWFS and DLS).}
  \label{fig:mcgreer}
\end{figure*}

\begin{landscape}
  \begin{table}
    % In published version of this table, we could remove file names and add data homogenisation in Notes.
    % Add z ~ 7 qso when you add it to analysis
    \caption{Quasar data sets}
    \label{tab:samples}
    \begin{tabular}{cccllcclll}
      \hline
      & ID & $z$ & Survey & Reference & Number & Area & Sample file & Selection map file & Notes \\
      & & & & & of quasars & (deg$^2$) & & & \\
      \hline
      1. & 13 & 0.1--2.2 & SDSS DR7 & \citet{2006AJ....131.2766R} & 48664 & 6248.0 & \texttt{dr7z2p2\_sample.dat} & \texttt{dr7z2p2\_selfunc.dat} &  \\
      2. & 15 & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 & \texttt{croom09sgp\_sample.dat} & \texttt{croom09sgp\_selfunc.dat} & \\ 
      3. &  2 & 0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 & \texttt{croom09ngp\_sample.dat} & \texttt{croom09ngp\_selfunc.dat} & \\
      4. &  1 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 & \texttt{bossdr9color.dat} & \texttt{ross13\_selfunc2.dat} & \\
      5. & 13 & 3.7--4.7 & SDSS DR7 & \citet{2006AJ....131.2766R} & 1785 & 6248.0 & \texttt{dr7z3p7\_sample.dat} & \texttt{dr7z3p7\_selfunc.dat} & Sample restricted to $z<4.7$ \\
      6. & 17 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 & \texttt{yang16\_sample.dat} & \texttt{yang16\_sel.dat} & Overlaps with 8 for $M_{1450}>-26.73$? \\
      7. &  8 & 4.7--5.1 & SDSS DR7 & \citet{2013ApJ...768..105M} & 148 & 6248.0 & \texttt{mcgreer13\_dr7sample.dat} & \texttt{mcgreer13\_dr7selfunc.dat} & \\
      8. &  4 & 4.7--5.1 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 52 & 235.0 & \texttt{mcgreer13\_s82sample.dat} & \texttt{mcgreer13\_s82selfunc.dat} & \\
      9. &  8 & 5.1--5.5 & --- DR7 Extended & \citet{2013ApJ...768..105M} & 28 & 6248.0 & \texttt{mcgreer13\_dr7extend.dat} & \texttt{mcgreer13\_dr7selfunc.dat} & \\
      10. & 4 & 5.1--5.4 & ---  Stripe 82 Extended & \citet{2013ApJ...768..105M} & 10 & 235.0 & \texttt{mcgreer13\_s82extend.dat} & \texttt{mcgreer13\_s82selfunc.dat} & \\
      11. & 3 & 3.7--4.8 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 & \texttt{glikman11qso.dat} & \texttt{glikman11\_selfunc\_ndwfs\_old.dat} & \\
%         &  &  &  &  &  &  & \texttt{glikman11debug.dat} & \texttt{glikman11\_selfunc\_ndwfs.dat} & \\ 
      12. & 6 & 3.8--5.1 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 & \texttt{glikman11qso.dat} & \texttt{glikman11\_selfunc\_dls\_old.dat} & \\
%      &  &  &  &  &  &  & \texttt{glikman11debug.dat} & \texttt{glikman11\_selfunc\_ndwfs.dat} & \\
      13. & 7 & 4.1--6.3 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 & \texttt{giallongo15\_sample.dat} & \texttt{giallongo15\_sel.dat} &  \\
      14. & 9 & 5.9--6.1 & SDSS Deep & \citet{2008AJ....135.1057J} & 6 & 260.0 & \texttt{jiang08\_sample.dat} & \texttt{jiang08\_sel.dat} \\
      15. & 5 & 5.8--6.0 & --- Deep & \citet{2009AJ....138..305J} & 4 & 195.0 & \texttt{jiang09\_sample.dat} & \texttt{jiang09\_sel.dat} \\
      16. & 18 & 5.8--6.4 & --- Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 & \texttt{jiang16main\_sample.dat} & \texttt{jiang16main\_selfunc.dat} \\
      17. & 16 & 5.8--6.4 & --- Main & \citet{2006AJ....131.1203F} & 14 & 6600.0 & \texttt{fan06\_sample.dat} & \texttt{fan06\_sel.dat} & Any overlap with 18? \\
      18. & 19 & 5.9--6.1 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 & \texttt{jiang16overlap\_sample.dat} & \texttt{jiang16overlap\_selfunc.dat} \\
      19. & 20 & 5.7--6.1 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 & \texttt{jiang16s82\_sample.dat} & \texttt{jiang16s82\_selfunc.dat} \\
      20. & 10 & 6.0 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 & \texttt{willott10\_cfhqsdeepsample.dat} & \texttt{willott10\_cfhqsdeepsel.dat} \\
      21. & 21 & 5.9--6.4 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 & \texttt{willott10\_cfhqsvwsample.dat} & \texttt{willott10\_cfhqsvwsel.dat} \\
      22. & 11 & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 & \texttt{kashikawa15\_sample.dat} & \texttt{kashikawa15\_sel.dat} \\

    \end{tabular}
  \end{table}
\end{landscape}

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z0.495}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z0.881}.pdf} \\

      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z1.252}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z1.626}.pdf} \\

      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z1.987}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.254}.pdf} \\
    \end{tabular}
  \end{center}
  \caption{Individual fits.  Something wrong with Croom's SGP data?}
\end{figure*}

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.348}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.446}.pdf} \\

      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.548}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.645}.pdf} \\

      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.746}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.901}.pdf} \\
    \end{tabular}
  \end{center}
  \caption{Individual fits.}
\end{figure*}

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z3.119}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z3.333}.pdf} \\

      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z3.831}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z4.196}.pdf} \\

      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z4.837}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z6.001}.pdf} \\
    \end{tabular}
  \end{center}
  \caption{Individual fits.}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{evolution.pdf}
  \end{center}
  \caption{Parameter evolution from individual fits.  Giallongo's qsos not included.}
\end{figure*}

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{pdflscape}
\usepackage{siunitx}

@@

  We model the quasar luminosity function as a double power law given
  by \citep{1988MNRAS.235..935B, 1995ApJ...438..623P, 2000MNRAS.317.1014B}
  \begin{equation}
    \phi(M) = \frac{\phi_*}{10^{0.4(\alpha+1)(M-M_*)}+10^{0.4(\beta+1)(M-M_*)}},
\label{eqn:dpl}
\end{equation}
where all magnitudes are absolute magnitudes at rest-frame 1450~{\AA}.  
The luminosity function $\phi$ gives the comoving number density of
quasars per unit magnitude.  It usually has units of
mag$^{-1}$cMpc$^{-3}$.  Equation~(\ref{eqn:dpl}) has four free
parameters: the amplitude $\phi_*$, the ``break'' $M_*$, the faint-end
slope $\beta$, and the bright-end slope $\alpha$.  The likelihood
function can be written as \citep{2001AJ....121...54F}
\begin{equation}
  \mathcal{L}=\prod_{i,j}\frac{e^{-\mu_{ij}}\mu_{ij}^{n_{ij}}}{n_{ij}!},
  \label{eqn:lhood}
\end{equation}
where $n_{ij}$ is the number of quasars observed in the $(M_i, z_j)$
bin, and
\begin{equation}
  \mu_{ij}= \int_{M_i}^{M_{i+1}}dM\int_{z_i}^{z_{i+1}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
\end{equation}
is the average number of quasars expected in the $(M_i, z_j)$ bin
given the luminosity function $\phi(M,z)$.  To obtain the maximum
likelihood solution for the luminosity functin parameters, we minimise
the function
\begin{equation}
  S = -2\ln\mathcal{L}.
\end{equation}
In the limit of infinitesimal bins, $n_{ij}=0$ or $1$, in which case
Equation~(\ref{eqn:lhood}) can be simplified and we can write \citep{1983ApJ...269...35M}
\begin{multline}
  S = -2\sum_{i=1}^N\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}dM\int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
\end{multline}
where $N$ is the total number of quasars in the sample and the
integral in the second term on the right hand side is now on the full
range of $M$ and $z$.

\section{Hydrogen photoionization rate}

We assume that all quasars have a universal SED, which can be
parameterised in some fashion.  \citet{2015MNRAS.449.4204L} have
parameterised the quasar SED as a power law with a break at 912~{\AA},
\begin{equation}
f_\nu\propto\begin{cases}
               \nu^{-0.61\pm 0.01} & \text{if}~\lambda\geq 912~\text{\AA},\\
               \nu^{-1.70\pm 0.61} & \text{if}~600~\text{\AA}<\lambda<912~\text{\AA}.\\                
               \end{cases}
\label{eqn:sed}
\end{equation}
Here $f_\nu$ is the flux density, with units of ergs s$^{-1}$
cm$^{-2}$ Hz$^{-1}$, although it is often simply called flux.  Note
that although $f_\nu$ is often the quantity of interest, e.g., when
calculating the hydrogen ionizing emissivity of quasars, what is shown
in spectra is often $f_\lambda$, the flux density
in \emph{wavelength}, which has units of ergs s$^{-1}$
cm$^{-2}$ \AA$^{-1}$.  If the flux density in frequency is power law,
then the flux density in wavelength is also power law.  The power law
index of the flux density in wavelength, $\alpha_\lambda$, is related
to the power law index of the flux density in frequency, $\alpha_\nu$,
by $\alpha_\lambda=-(\alpha_\nu+2)$.  From Equation~(\ref{eqn:sed}),
we can now see that $\alpha_\lambda=-0.3$ in the extreme UV (EUV;
600~{\AA}$<\lambda<$912~{\AA}) and $\alpha_\lambda=-1.39$ in the far
UV (FUV; $\lambda>$912~{\AA}).  The quasar SED that we have adopted is
steep in FUV and shallow in EUV.

How sensible is it to assume that the quasar SED of
Equation~(\ref{eqn:sed}) is universal?  Of the four published
composite quasar SEDs (see references in
\citealt{2015MNRAS.449.4204L}), three agree with
Equation~(\ref{eqn:sed}).  There is one published composite quasar SED
that does not agree with Equation~(\ref{eqn:sed}).  This is the
composite of \citet{2004ApJ...615..135S}, which uses more than 100
quasars at $z<0.1$.  The EUV slope of this SED is $-0.56$.  (This
means that the power law index of the flux density in wavelength is
$-1.44$, so that the spectrum actually becomes even steeper in the
EUV.  See Figure 8 of \citealt{2015MNRAS.449.4204L}.)  The quasars
considered by \citet{2004ApJ...615..135S} are much fainter that those
considered by \citet{2015MNRAS.449.4204L}, which means that it is
possible that faint quasars have a steep EUV spectrum.  So we could
say that for faint quasars,
\begin{equation}
f_\nu\propto\begin{cases}
               \nu^{-0.61\pm 0.01} & \text{if}~\lambda\geq 912~\text{\AA},\\
               \nu^{-0.56\pm 0.61} & \text{if}~600~\text{\AA}<\lambda<912~\text{\AA}.\\                
               \end{cases}
\label{eqn:sed_faint}
\end{equation}
Here, ``faint'' is defined as $M_i(z=2)>-26$.  $M_i(z=2)$ can be
related to the bolometric luminosity of the quasar (see Figure 9 of
\citealt{2015MNRAS.449.4204L}.)

The rate of emission of photons of frequency $\nu$ by quasars can be
written as
\begin{equation}
\dot n_\nu = \int dM_\nu \phi(M_\nu) \frac{L_\nu(M_\nu)}{h\nu}.
\end{equation}
The units of $\dot n_\nu$ are s$^{-1}$~cMpc$^{-3}$~Hz$^{-1}$.  Here
the integral is over some range of magnitudes, the monochromatic
luminosity $L_\nu(M)$ is related to the (absolute AB) magnitude
by \citep{1983ApJ...266..713O}
\begin{equation}
M_\nu = -2.5\log_{10}L_\nu+51.60,
\end{equation}
and $\phi$ is the luminosity function from Equation~(\ref{eqn:dpl}).
The luminosity at 1~Ry is related to that at 1450~\AA\ by
Equation~(\ref{eqn:sed}) or (\ref{eqn:sed_faint})
\begin{equation}
  L_{912}=L_{1450}\left(\frac{\nu_{912}}{\nu_{1450}}\right)^{-0.61}=L_{1450}\left(\frac{912}{1450}\right)^{0.61}
\end{equation}
The corresponding volume emissivity is conventionally written
as 
\begin{equation}
\epsilon_\nu = \dot n_\nu h\nu (1+z)^3.
\label{eqn:epsilon}
\end{equation}
This is a \emph{physical} density.  The units of $\epsilon_\nu$ are
erg~s$^{-1}$~pMpc$^{-3}$~Hz$^{-1}$.  This emissivity can now be used
to calculate the ionizing flux and photoionization rate contributed by
quasars.  The frequency dependence above 1~Ry is given by
Equation~(\ref{eqn:sed}) or (\ref{eqn:sed_faint}), so that for $\nu >
\nu_{912}$
\begin{equation}
  \epsilon_\nu = \epsilon_{912}\left(\frac{\nu}{\nu_{912}}\right)^\alpha,
  \label{eqn:epsilon_freq}
\end{equation}
where $\alpha=-1.70$ (Equation~\ref{eqn:sed}) or $-0.56$ (Equation~\ref{eqn:sed_faint}).

The emissivity calculated in Equation~(\ref{eqn:epsilon}) is a source
property.  We are now interested in what flux this emissivity produces
in the surrounding intergalactic medium.  This brings in the medium's
properties also, via the radiative transfer equation.  The flux is
\citep{2012ApJ...746..125H}
\begin{multline}
  j(\nu_0, z_0)=\frac{1}{4\pi}\int_{z_0}^\infty dz\frac{dl}{dz}\frac{(1+z_0)^3}{(1+z)^3}\epsilon(\nu,z)\\
  \times\exp{(-\tau_\mathrm{eff}(\nu_0, z_0, z))},
  \label{eqn:flux}
\end{multline}
where
\begin{equation}
  \nu = \nu_0\left(\frac{1+z}{1+z_0}\right).
\end{equation}
We estimate the effective optical depth as
\begin{equation}
  \tau_\mathrm{eff}(\nu_0, z_0, z) = \int_{z_0}^z dz^\prime\int_0^\infty dN_\mathrm{HI} f(N_\mathrm{HI}, z^\prime) (1-e^{-\tau_\nu}),
\end{equation}
where $\tau_\nu=\sigma_\nu N_\mathrm{HI}$ and the column density
distribution $f(N_\mathrm{HI}, z)$ is taken to be a power law \citep{2013MNRAS.436.1023B}
\begin{equation}
  f(N_\mathrm{HI}, z) = \frac{A}{N_\mathrm{LL}}\left(\frac{N_\mathrm{HI}}{N_\mathrm{LL}}\right)^{-\beta_N}\left(\frac{1+z}{4.5}\right)^{-\beta_z},
\end{equation}
with $A=0.93$, $\beta_N=1.33$, $\beta_z=1.92$, and
$N_\mathrm{LL}=10^{17.2}$~cm$^{-2}$.  The hydrogen photoionization
rate is then given by
\begin{equation}
  \Gamma_\mathrm{HI}=4\pi\int_{\nu_{912}}^\infty d\nu \frac{j(\nu,z)}{h\nu} \sigma(\nu),
\end{equation}

\subsection{Local source approximation}

In the local source approximation, Equation~(\ref{eqn:flux}) becomes
\begin{equation}
  j(\nu_0, z_0) = \frac{1}{4\pi}\lambda_\mathrm{mfp}(\nu_0, z_0)\epsilon(\nu_0, z_0),
\end{equation}
where $\lambda_\mathrm{mfp}$ is the mean free path.  The hydrogen
photoionization rate is given by
\begin{equation}
  \Gamma_\mathrm{HI}=4\pi\int_{\nu_{912}}^\infty d\nu \frac{j_\nu}{h\nu} \sigma(\nu),
  \label{eqn:gammapi}
\end{equation}
where $\sigma$ is the ionization cross-section
\begin{equation}
  \sigma(\nu) = \sigma_0\left(\frac{\nu}{\nu_{912}}\right)^{-3},
  \label{eqn:sigma}
\end{equation}
with $\sigma_0=6.3\times 10^{-18}$~cm$^2$ \citep{2006agna.book.....O}.
In the redshift range $z=2.3$--$5.5$, the mean free path is measured
to be \citep{2014MNRAS.445.1745W}
\begin{equation}
  \lambda_\mathrm{mfp}(\nu, z)= \lambda_0\left(\frac{1+z}{5}\right)^{-5.4}\left(\frac{\nu}{\nu_{912}}\right)^{1.5},
  \label{eqn:mfp}
\end{equation}
where the frequency dependence comes from the assumed column density
distribution $f(N_\mathrm{HI})\propto N_\mathrm{HI}^{-1.5}$.  We
extrapolate the redshift dependence in Equation~(\ref{eqn:mfp}) at
$z<2.3$ and $z>5.5$.  Combining Equations~(\ref{eqn:epsilon_freq}),
(\ref{eqn:sigma}), and (\ref{eqn:mfp}), Equation~(\ref{eqn:gammapi})
gives
\begin{multline}
  \Gamma_\mathrm{HI}=4.6\times 10^{-13} \mathrm{s}^{-1} \left(\frac{\epsilon_{912}}{10^{24}\mathrm{erg s^{-1} Hz^{-1} cMpc^{-3}}}\right)\\
  \times\left(\frac{1}{1.5-\alpha}\right)\left(\frac{1+z}{5}\right)^{-2.4}.
\end{multline}
Note that this equation refers to the \emph{comoving} emissivity.  The
local source approximation works well for $z>3$ \citep{2013MNRAS.436.1023B}.

\begin{table*}
  % In published version of this table, we could remove file names and add data homogenisation in Notes.
  % Add z ~ 7 qso when you add it to analysis
  % See data.tex for a version of this table that includes file names
  \caption{Quasar data sets}
  \label{tab:samples}
  \begin{tabular}{crcllrSl}
    \hline
    & ID & $z$ & Survey & Reference & Number & {Area} & Notes \\
    & & & & & of quasars & {(deg$^2$)} & \\
    \hline
    1. & 13 & 0.1--2.2 & SDSS DR7 & \citet{2006AJ....131.2766R} & 48664 & 6248.0 & \\
    2. & 15 & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 & \\
    3. & 15  & 0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 & \\
    4. &  1 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 & \\
    5. & 13 & 3.7--4.7 & SDSS DR7 & \citet{2006AJ....131.2766R} & 1785 & 6248.0 & Restricted to $z<4.7$ \\
    6. & 17 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 & Overlaps with 8 for $M_{1450}<-26.73$ \\
    7. &  8 & 4.7--5.1 & SDSS DR7 & \citet{2013ApJ...768..105M} & 148 & 6248.0 & \\
    8. &  8 & 4.7--5.1 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 52 & 235.0 & \\
    9. &  8 & 5.1--5.5 & --- DR7 Extended & \citet{2013ApJ...768..105M} & 28 & 6248.0 & \\
    10. & 8 & 5.1--5.4 & ---  Stripe 82 Extended & \citet{2013ApJ...768..105M} & 10 & 235.0 & \\
    11. & 6 & 3.7--4.8 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 & \\
    12. & 6 & 3.8--5.1 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 & \\
    13. & 7 & 4.1--6.3 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 & Rescaled selection probabilities \\
    14. & 18 & 5.8--6.4 & --- Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 & \\
    15. & 18 & 5.9--6.1 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 & \\
    16. & 18 & 5.7--6.1 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 & \\
    17. & 10 & 6.0 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 & \\
    18. & 10 & 5.9--6.4 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 & \\
    19. & 11 & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 & \\
  \end{tabular}
\end{table*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{sdss.pdf}
  \end{center}
  \caption{Comparison with the published LF of
    \citet{2006AJ....131.2766R} for SDSS DR3.  There are 15,343
    quasars in this sample, of which 155 quasars have $z<0.3$ and 9
    quasars have $z>5$.  Of the remaining 15179 quasars with
    $0.3<z<5$, 60 quasars have $V_i=0$ and are dropped from the
    analysis.  As a result, the green points above contain 15,119
    quasars.  The red circles contain 14,953 quasars.}
  \label{fig:sdss}
\end{figure*}

@@

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[width=0.6\textwidth,keepaspectratio]{glikman.pdf}
%%   \end{center}
%%   \caption{Comparison with the published LF of
%%     \citet{2011ApJ...728L..26G} for $3.5<z<5.2$.  There are 24 
%%     quasars in their two samples (NDWFS and DLS).}
%%   \label{fig:mcgreer}
%% \end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{glikman3.pdf}
  \end{center}
  \caption{Attempts at reproducing Glikman's published LF.  Panels (a)
    and (b) use her volume calculations.  Panels (c)--(e) use our
    volume calculations.  Various corrections incorporated by Gabor
    are in panels (c)--(e).  Red open circles in all panels are
    Glikman's published values; I cannot reproduce them in any of the
    panels.  All luminosity function in this version of the draft use
    Gabor's October data from panel (d).}
  \label{fig:glikman}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{giallongo2.pdf}
  \end{center}
  \caption{Giallongo's LF when selection function is taken to be
    $\phi_\mathrm{corr}/\phi$ from their paper.  This plots shows that
    additional correction is required, which has been incorporated in
    our LFs.}
  \label{fig:giallongo}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic.pdf}
  \end{center}
  \caption{Luminosity function for $z=0.3$ to $2.6$.}
  \label{fig:mosaic}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic2.pdf}
  \end{center}
  \caption{Luminosity function for $z=2.6$ to $6.5$.}
  \label{fig:mosaic2}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{evolution.pdf}
  \end{center}
  \caption{Parameter evolution from individual fits.  Coloured points
    show results when Giallongo quasars are not included.  Black
    points show results when Giallongo quasars are included.}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.6\textwidth,keepaspectratio]{gammapi.pdf}
  \end{center}
  \caption{Hydrogen photoionization rate}
  \label{fig:gammapi}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.6\textwidth,keepaspectratio]{emissivity.pdf}
  \end{center}
  \caption{LyC emissivity.}
  \label{fig:gammapi}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{evolution_global.pdf}
  \end{center}
  \caption{One possible global fit with a 12-parameter model.  Each
    double power law parameter has a 4th-order Chebyshev polynomial
    form.  Black points show result from Manti et al.~2017.}
  \label{fig:global_fit}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso.pdf}
  \end{center}
  \caption{Shouldn't there be cosmic downsizing?}
  \label{fig:rhoqso}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
  \end{center}
  \caption{Same as Figure~\ref{fig:rhoqso} but now with the global model.  This global model is the same as that shown in Figure~\ref{fig:global_fit}.}
  \label{fig:rhoqso_withGlobal}
\end{figure*}

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[width=\textwidth,keepaspectratio]{triangle.png}
%%   \end{center}
%%   \caption{Posteriors corresponding to Figure~\ref{fig:global_fit}.}
%%   \label{fig:triangle}
%% \end{figure*}

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[height=\textheight]{chains.pdf}
%%   \end{center}
%%   \caption{MCMC chains corresponding to Figure~\ref{fig:global_fit}.}
%%   \label{fig:chains}
%% \end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{evolution_cleaned.pdf}
  \end{center}
  \caption{Parameter evolution after making two changes to the
    analysis: (1) use \emph{only} BOSS quasars for $z=2.2$--$3.5$, and
    (2) use only $p>0.9$ quasars in the $z>3.7$ sample of Richards.
    The individual fits with these changes are shown in Figures
    \ref{fig:mosaic} and \ref{fig:mosaic2}.}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{evolution_model1.pdf}
  \end{center}
  \caption{My current global fit.  I am trying to understand why it is
    so bad.  See Figures~17--21 for more on this.  Note that now I am
    only trying to fit quasars with $z=0.6$--$2.2$ and $2.8$--$5.5$.
    I am trying to fit straight lines for $M_*$ and $\alpha$ and
    quadratics for $\phi_*$ and $\beta$.}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_model1.pdf}
  \end{center}
  \caption{The global fit is quite good at $z\sim 1$--$2$.}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth,keepaspectratio]{mosaic2_model1.pdf}
  \end{center}
  \caption{Previous figure continued.}
\end{figure*}

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[height=\textheight,keepaspectratio]{chains_model1.pdf}
%%   \end{center}
%%   \caption{MCMC chains for the global model of Figures~16--18.}
%% \end{figure*}

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[width=\textwidth,keepaspectratio]{triangle_model1.png}
%%   \end{center}
%%   \caption{Posteriors for the global model of Figures~16--18.}
%% \end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso_model1.pdf}
  \end{center}
  \caption{Quasar number density in the global model of Figure~16.}
\end{figure*}
